---
title: "Apresentação"
author: "Rafael Felipe Bressan"
date: "29 de junho de 2018"
output: 
  ioslides_presentation:
    theme: journal
    incremental: true
    #logo: Marca_Udesc.jpeg
    css: https://bootswatch.com/4/journal/bootstrap.min.css
---
<!-- Temas que podem ser utilizados a partir do CSS
'Default'='https://netdna.bootstrapcdn.com/bootstrap/3.0.0/css/bootstrap.min.css',
'Amelia'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/amelia/bootstrap.min.css',
'Cerulean'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/cerulean/bootstrap.min.css',
'Cosmo'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/cosmo/bootstrap.min.css',
'Cyborg'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/cyborg/bootstrap.min.css',
'Journal'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/journal/bootstrap.min.css',
'Flatly'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/flatly/bootstrap.min.css',
'Readable'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/readable/bootstrap.min.css',
'Simplex'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/simplex/bootstrap.min.css',
'Slate'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/slate/bootstrap.min.css',
'Spacelab'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/spacelab/bootstrap.min.css',
'United'='https://netdna.bootstrapcdn.com/bootswatch/3.0.0/united/bootstrap.min.css'

Highlights
'HighlightJs'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/default.min.css'
'Dark'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/dark.min.css',
'Far'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/far.min.css',
'Idea'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/idea.min.css',
'Sunburst'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/sunburst.min.css',
'Zenburn'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/zenburn.min.css',
'Visual Studio'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/vs.min.css',
'Ascetic'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/ascetic.min.css',
'Magula'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/magula.min.css',
'Github'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/github.min.css',
'Google Code'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/googlecode.min.css',
'Brown Paper'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/brown_paper.min.css',
'School Book'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/school_book.min.css',
'IR Black'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/ir_black.min.css',
'Solarized - Dark'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/solarized_dark.min.css',
'Solarized - Light'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/solarized_light.min.css',
'Arta'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/arta.min.css',
'Monokai'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/monokai.min.css',
'Xcode'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/xcode.min.css',
'Pojoaque'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/pojoaque.min.css',
'Rainbow'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/rainbow.min.css',
'Tomorrow'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/tomorrow.min.css',
'Tomorrow Night'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/tomorrow-night.min.css',
'Tomorrow Night Bright'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/tomorrow-night-bright.min.css',
'Tomorrow Night Blue'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/tomorrow-night-blue.min.css',
'Tomorrow Night Eighties'='https://cdnjs.cloudflare.com/ajax/libs/highlight.js/7.3/styles/tomorrow-night-eighties.min.css'

-->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown {data-background=risk1.jpg data-background-size=cover}

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with code only

```{r code, eval=FALSE, echo=TRUE}
x <- rnorm(100)
plot(seq_along(x), x)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

